Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-07 ms.tex
conclusions 6
marking out solutions which are unstable for some values of eta.

  {$\left(\frac{\dot{q}_{\rm heat}}{|\dot{q}_{\rm rad}|}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Issues? \\

@@

$    10^{ 7 }$ & 300 & 25 & 0.42 & $ 2.4 \times 10^{ -4 }$ & 7 \\
... & ... & 50 & 0.38 & $ 2.0 \times 10^{ -4 }$ & 4.5 \\

@@

$    10^{ 8 }$ & 300 & 25 & 0.69 & $ 4.2 \times 10^{ -4 }$ & 5.5 \\
... & ... & 50 & 0.92 & $ 6.0 \times 10^{ -4 }$ & 2 \\

@@

... & 1200 & 25 & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\

@@

$    10^{ 7 }$ & 600 & 25 & 0.19 & $ 2.9 \times 10^{ -5 }$ & 79 \\

@@

... & ... & 50 & 0.46 & $ 1.5 \times 10^{ -4 }$ & 9.4 \\

@@

  saturation parameter $\phi = 0.1$ (recall that the
  conductive heat flux saturates to $F_{\rm cond}=5\phi \rho c_s^3$).  Entries for solutions found to be thermally unstable for all values of $\eta > 0.02$ are denoted as {\bf TI}.

@@

>>>>

  {$\left(\frac{\dot{q}_{\rm heat}}{|\dot{q}_{\rm
          rad}|}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Unstable
  $\eta$'s  \\

@@

$    10^{ 7 }$ & 300 & 25 & 0.42 & $ 2.4 \times 10^{ -4 }$ & 7 & 0.2, 0.6\\ 
... & ... & 50 & 0.38 & $ 2.0 \times 10^{ -4 }$ & 4.5 & 0.2, 0.6\\

@@

$    10^{ 8 }$ & 300 & 25 & 0.69 & $ 4.2 \times 10^{ -4 }$ & 5.5 & 0.6\\
... & ... & 50 & 0.92 & $ 6.0 \times 10^{ -4 }$ & 2 & 0.6\\

@@

... & 1200 & -- & $ 1.5 \times 10^{ -2 }$ & $ 2.3 \times 10^{ -7 }$ & $ 1.7 \times 10^{ 5 }$ \\

@@

$    10^{ 7 }$ & 600 & 25 & 0.19 & $ 2.9 \times 10^{ -5 }$ & 79 & 0.6 \\

@@

... & ... & 50 & 0.46 & $ 1.5 \times 10^{ -4 }$ & 9.4 & 0.2, 0.6\\

@@

  saturation parameter $\phi = 0.1$ (recall that the conductive heat
  flux saturates to $F_{\rm cond}=5\phi \rho c_s^3$). We ran solutions
  with radiative cooling for all cusp galaxies with $v_w=300 $ km/s
  and all core galaxies with $v_w=600 $ km/s with three different
  values of the mass loss parameter $\eta$: 0.02, 0.2, and 0.6. Any
  values of $\eta$ for which a solution turned out to be thermally
  unstable are marked in the ``Unstable $\eta$'s'' column.  Entries
  for solutions found to be thermally unstable for all values of $\eta
  > 0.02$ are denoted as {\bf TI}.

@@

\item Radiative cooling has a more pronounced influence on the structure of the gas flow.  The approximate condition for cooling instabilities develop is that the rate of radiative cooling exceed the external heating rate at the stagnation radius.
